---
title: "Weight of Fish"
author: "Addler Fuller"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
require(leaps)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.


## Perch
```{r}
fullup <- lm(Weight~ .,data=Perch)
summary.lm(fullup)
```

### Best Models
The data shows the Adjusted R-squared has the better model for Length. From the data gather we have determine the summary has p-value of 2.2e-16.

### Best Two regressor model
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottom",main="Adjusted R^2")
```


Now using the chart above, we have analysis the data gather that the two best regression model are height and width.

## Pike
```{r}
fullup <- lm(Weight~ .,data=Pike)
summary.lm(fullup)
```

### Best Models
This data shows that the best models are L-1, L-2, L-3, factor of height and weight> The P-vaule of this chart is 8.679e-10.

### Best Two regressor model
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```


They given us the two best element of the data are L-1, L-3W.


## Roach

```{r}
fullup <- lm(Weight~ .,data=Roach)
summary.lm(fullup)
```

### Best Models
The best model that it shown is L-3 being Width instead of Weight. The P-value is 1.028e-05

### Best Two regressor model

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```


The best regression summary would be L-3 and Width.




## Final Summary Statements

After reviewing all the data we have gather from Porch, Pike, and roach, from using a leap program to figure out whats the best regression model, leaps helped us display all the data like for explain adjusted R-squared was for us to compare width or weight to see what impact it and the outcome of the data for it. 
